\textbf{Access Control for Content Distribution Network Assets}

### 2016-05-13 tex/paper.tex
Fixed faulty font on access rights
Added the meta variable for changing containers

To describe a content object \textit{m} containing fileId \textit{f}, the following syntax is used:
$\{id = \dots , file = f\} \in M$, the same syntax is also applied to different types of objects
throughout the explanation of the model. The \"fresh\" keyword applied to id means that it is a new
globally unique identifier.

If the user is irrelevant for the rule described, it is left out from the action, for example u,
read(o) = read(o).

\vspace{1em}
The following predicates are used in several places and are therefore named \textit{*} to avoid
unnecessary repetition.
\begin{equation} \label{eq:fileread}
    \inferrule
    {(\textbf{*}) \\ C \ni c \ni m \\ $A[u,c]$} 
    {}
\end{equation}
\vspace{1em}

\vspace{2em}
\textbf{File Read}
\vspace{1em}
\begin{equation} \label{eq:fileread}
    \inferrule
    {(\textbf{*})} 
    {(C, F) \xrightarrow{u, read(m,f)} (C, F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{File Creation}
\vspace{1em}
\begin{equation} \label{eq:filecreate}
    \inferrule
    {C \ni c \\ $A[u,c]$ \\ m \centernot \in c \\ \neg readOnly(c)} 
    {(C \cup \{c\}, F) \xrightarrow{u, create(m,c)} (C \cup \{c \cup \{m\}\}, F \cup \{m.file\})}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{File Update}
\vspace{1em}
\begin{equation} \label{eq:fileupdate}
    \inferrule
    {\textbf{*} \\ c' = c \cup \{m'\} \\ m' = \{id = m.id, file = f'\} \\ \neg readOnly(c)} 
    {(C \cup \{c \cup \{m\}\} , F) \xrightarrow{u, update(m, f')} (C \cup \{c \cup \{m'\}\}, F
    \cup \{f'\}))}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Update}
\vspace{1em}
\begin{equation} \label{eq:contentupdate}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C \cup \{c \cup \{m\}\}, F) \xrightarrow{u, update(m, m')} ((C \cup \{c \cup \{m'\}\}, F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Container Update}
\vspace{1em}
\begin{equation} \label{eq:containerupdate}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C \cup \{c\}, F) \xrightarrow{u, update(c, c')} (C \cup \{c'\}, F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Copy}
\vspace{1em}
\begin{equation} \label{eq:copy}
    \inferrule
    {\textbf{*} \\ m' = \{id = \text{"fresh"}, file = m.file\} \\ \neg readOnly(c)}
    {(C \cup \{c \cup \{m\}\}, F) \xrightarrow{u, create(c, m')} (C \cup \{c \cup \{m, m'\}\}, F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Deletion}
\vspace{1em}
\begin{equation} \label{eq:delete}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C \cup \{m\}, F) \xrightarrow{u, delete(m)} (C, F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\begin{equation} \label{eq:snapshot2}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C, F) \xrightarrow{[C', M'] := u, snapshot(c)} (C \cup C' \cup M', F)}
\end{equation}
If a user creates a snapshot of a container and the full container tree is re-created with new IDs,
but its content still refers to the same files.

@@

\subsection{Findings}
This section summarises the findings from the work on the model.

@@

\hfill \\
\textbf{REST Endpoints} \label{sec:API} \hfill \\
For the front-end to communicate with the back-end, a RESTful service is implemented.
The following endpoints were configured:

@@

\newpage
\section{Summary}
This section covers the conclusions that I draw from this work and how I plan to extend the
implementation in the future.

@@

>>>>

To describe a content object \textit{m} containing fileId \textit{f}, the following syntax is used:
$\{id = \dots , file = f\} \in M$, the same syntax is also applied to different types of objects
throughout the explanation of the model. The ``fresh'' keyword applied to id means that it is a new
globally unique identifier.

To explain a change of a container the notation $C[c]$ is used when removing or adding a nested
container from the set. $C[\cdot]$ is a \textit{C} that can contain the meta variable $\cdot$ and
$C[c]$ is $C[\cdot]$ where $\cdot$ has been replaced by \textit{c}.

\vspace{1em}
The following predicates are used in several places and are therefore named \textit{*} to avoid
unnecessary repetition.
\begin{equation} \label{eq:predicate_rules}
    \inferrule
    {(\textbf{*}) \\ C \ni c \ni m \\ A[u,c]} 
    {}
\end{equation}

\vspace{1em}
\textbf{File Read}
\vspace{1em}
\begin{equation} \label{eq:fileread}
    \inferrule
    {(\textbf{*})} 
    {(C, F) \xrightarrow{u, read(m,f)} (C, F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{File Creation}
\vspace{1em}
\begin{equation} \label{eq:filecreate}
    \inferrule
    {C \ni c \\ A[u,c] \\ m \centernot \in c \\ \neg readOnly(c)} 
    {(C[c], F) \xrightarrow{u, create(m,c)} (C[c \cup \{m\}], F \cup \{m.file\})}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{File Update}
\vspace{1em}
\begin{equation} \label{eq:fileupdate}
    \inferrule
    {\textbf{*} \\ c' = c \cup \{m'\} \\ m' = \{id = m.id, file = f'\} \\ \neg readOnly(c)} 
    {(C[c \cup \{m\}], F) \xrightarrow{u, update(m, f')} ((C[c \cup \{m'\}], F \cup \{f'\}))}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Update}
\vspace{1em}
\begin{equation} \label{eq:contentupdate}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C[c \cup \{m\}], F) \xrightarrow{u, update(m, m')} ((C[c \cup \{m'\}], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\newpage
\textbf{Container Update}
\vspace{1em}
\begin{equation} \label{eq:containerupdate}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C[c], F) \xrightarrow{u, update(c, c')} (C[c'], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Copy}
\vspace{1em}
\begin{equation} \label{eq:copy}
    \inferrule
    {\textbf{*} \\ m' = \{id = \text{"fresh"}, file = m.file\} \\ \neg readOnly(c)}
    {(C[c \cup \{m\}], F) \xrightarrow{u, create(c, m')} (C[c \cup \{m, m'\}], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\textbf{Content Deletion}
\vspace{1em}
\begin{equation} \label{eq:delete}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C[m], F) \xrightarrow{u, delete(m)} (C[], F)}
\end{equation}
\vspace{1em}

@@

\vspace{2em}
\begin{equation} \label{eq:snapshot2}
    \inferrule
    {\textbf{*} \\ \neg readOnly(c)}
    {(C, F) \xrightarrow{[C', M'] := u, snapshot(c)} (C[C' \cup M'], F)}
\end{equation}
If a user creates a snapshot of a container and the full container tree is re-created with new IDs,
but its content still refers to the same files.

@@

\newpage
\subsection{Findings}
This section summarises the findings from the work on the model.

@@

\hfill \\
\newpage
\textbf{REST Endpoints} \label{sec:API} \hfill \\
For the front-end to communicate with the back-end, a RESTful service is implemented.
The following endpoints were configured:

@@

\newpage

\newgeometry{top=4cm}
\section{Summary}
This section covers the conclusions that I draw from this work and how I plan to extend the
implementation in the future.

@@

\restoregeometry
